### 2023-05-31 paper/localpsf.tex
update adv table to use 1e-6 tolerance

>>>>

\begin{figure}
	\begin{center}
		\begingroup
		\setlength{\tabcolsep}{8pt}
		\renewcommand{\arraystretch}{1.25}
		\begin{tabular}{c| c | c c c c c}
			& $\kappa$    & REG     &	NONE   & PSF $(1)$ & PSF $(5)$ & PSF $(25)$ \\ 
			\hline 
			& $1.0e-4$    & 584 & 317  & 311   & 151   & 56    \\ 
			& $1.8e-4$    & 628 & 313  & 192   & 131   & 49    \\   
	$T=0.5$ & $3.2e-4$    & 685 & 311  & 233   & 140   & 44    \\ 
			& $5.6e-4$    & 734 & 310  & 334   & 144   & 40    \\  
			& $1.0e-3$    & 702 & 324  & 122   & 71   & 33    \\ 
			\hline
			& $1.0e-4$    & 634 & 449  & 539   & 288   & 100    \\ 
			& $1.8e-4$    & 665 & 449  & 493   & 212   & 84    \\   
	$T=1.0$ & $3.2e-4$    & 681 & 459  & 350   & 202   & 90    \\ 
			& $5.6e-4$    & 619 & 482  & 262   & 197   & 70    \\  
			& $1.0e-3$    & 574 & 520  & 266   & 260   & 208    \\ 
			\hline
			& $1.0e-4$    & 609 & 591  & 548   & 520   & 165    \\ 
			& $1.8e-4$    & 576 & 611  & 434   & 426   & 185    \\   
	$T=2.0$ & $3.2e-4$    & 524 & 645  & 318   & 379   & 170    \\ 
			& $5.6e-4$    & 464 & 711  & 480   & 289   & 153    \\  
			& $1.0e-3$    & 349 & 786  & 381   & 262   & 158    \\ 
		\end{tabular}
		\endgroup
	\end{center}
	\caption{Number of preconditioned conjugate gradient iterations to achieve tolerance $10^{-6}$ for solving the Newton linear system in the advection-diffusion inverse problem. Iteration counts are shown for a variety of different diffusion parameters $\kappa$, simulation times $T$, and preconditioners.}
	\label{tab:adv_convergence}
\end{figure}
